Titulo

### 2015-03-18 Paper/ms.tex
fixing galaxy parameters

>>>>

\subsubsection{Galaxy Parameters}

Our aim is to provide a realistic baseline to compare against
observations of LAES at $z\sim 3$. 
It has been found by analysis of the abundance and angular correlation
function that LAES reside in DM halos of masses in the range
$10^{10}-10^{11}$\Msun \cite{WalkerSoler2012}. 
This mass range corresponds to maximum circular velocities in the
range $60-125$\kms and a median halo scale radius of
$15$kpc. Considering that these galaxies are gas dominated we
approximate their neutral hydrogen gas contents has half their total
baryonic content estimated from the cosmological baryon to dark matter
abundances $\Omega_b/\Omega_{dm}=0.1825$ \citep{Planck2015}, which
gives us gaseous masses in the range $10^{9}-10^{10}$\Msun.

\footnote{These results were found using the N-body data
  available in \url{www.cosmosim.org}}.

From these constraints we chose to model our galaxies as sphere of
radius $15$kpc and rotation velocities in the range
$60-125$\kms.
